\MakeUppercase{Graph Product Structure for Non-Minor-Closed Classes}

### 2022-10-18 k-planar.tex
added a  sentence to the mao graph proof
fixed a bib entry

If $G_0$ has a face $f$ of length 2, then add a new vertex inside $f$ adjacent to both vertices on the boundary of $f$, which creates two new triangular faces $f_1$ and $f_2$. If $f$ is a lake, then make $f_1$ and $f_2$ lakes. If $F$ is a nation, then make $f_1$ a nation and make $f_2$ a lake. The resulting map graph is still $M$. So we may assume that $G_0$ is an edge-maximal multigraph with no faces of length 2 (and with each face labelled a nation or a lake), such that $G$ is the corresponding map graph. Suppose that some face $f$ of $G_0$ has a disconnected boundary (implying $G_0$ is disconnected). Let $v$ and $w$ be vertices in distinct components of the boundary of $f$. Add the edge $vw$ to $G_0$ across $f$. The corresponding map graph is unchanged, which contradicts the edge-maximality of $G_0$. Thus no face of $G_0$ is disconnected. Suppose that some face $f$ of $G_0$ has a repeated vertex in the boundary walk of $f$. Let $u,v,w$ be consecutive vertices on the boundary of $f$. So $u,v,w$ are distinct and $uw$ is not an edge in the boundary of $f$. Add the edge $uw$ across $f$ and consider the resulting face $uvw$ to be a lake. Since $v$ appears elsewhere in the boundary of $f$, the corresponding map graph is unchanged, which contradicts the edge-maximality of $G_0$. Thus no facial walk of $G_0$ has a repeated vertex. Since each facial walk is connected, every face of $G_0$ is bounded by a cycle, and $G_0$ is biconnected.

@@

	\bibitem[{Ueckerdt et~al.(2021)Ueckerdt, Wood, and Yi}]{UWY}
	\textsc{Torsten Ueckerdt, David~R. Wood, and Wendy Yi}.
	\newblock \href{http://arxiv.org/abs/2108.00198}{An improved planar graph
		product structure theorem}.
	\newblock 2021, arXiv:2108.00198.

>>>>

If $G_0$ has a face $f$ of length 2, then add a new vertex inside $f$ adjacent to both vertices on the boundary of $f$, which creates two new triangular faces $f_1$ and $f_2$. If $f$ is a lake, then make $f_1$ and $f_2$ lakes. If $F$ is a nation, then make $f_1$ a nation and make $f_2$ a lake. The resulting map graph is still $G$. So we may assume that $G_0$ is an edge-maximal multigraph with no faces of length 2 (and with each face labelled a nation or a lake), such that $G$ is the corresponding map graph. This is well-defined since the assumption of having no face of length 2 implies that $|E(G_0|\leq 3|V(G)|-6$.

Suppose that some face $f$ of $G_0$ has a disconnected boundary (implying $G_0$ is disconnected). Let $v$ and $w$ be vertices in distinct components of the boundary of $f$. Add the edge $vw$ to $G_0$ across $f$. The corresponding map graph is unchanged, which contradicts the edge-maximality of $G_0$. Thus no face of $G_0$ is disconnected. Suppose that some face $f$ of $G_0$ has a repeated vertex in the boundary walk of $f$. Let $u,v,w$ be consecutive vertices on the boundary of $f$. So $u,v,w$ are distinct and $uw$ is not an edge in the boundary of $f$. Add the edge $uw$ across $f$ and consider the resulting face $uvw$ to be a lake. Since $v$ appears elsewhere in the boundary of $f$, the corresponding map graph is unchanged, which contradicts the edge-maximality of $G_0$. Thus no facial walk of $G_0$ has a repeated vertex. Since each facial walk is connected, every face of $G_0$ is bounded by a cycle, and $G_0$ is biconnected.

@@

	\bibitem[{Ueckerdt et~al.(2021)Ueckerdt, Wood, and Yi}]{UWY}
	\textsc{Torsten Ueckerdt, David~R. Wood, and Wendy Yi}.
	\newblock \href{https://doi.org/10.37236/10614}{An improved planar graph product structure theorem}.
	\newblock Electronic J. Combinatorics 29:P2.51, 2022.
